Update after major correction to *Management induced changes of soil organic carbon on global croplands*

### 2021-08-09 ResultNotebooks/investigate_SOCbugfixDiff.Rmd
update results

---
title: "Update after major correction to *Management induced changes of soil organic carbon on global croplands*"
author: "Kristine Karstens"
date: "June 8, 2021"
output: pdf_document
rmarkdown::pdf_document:
  fig_caption: yes
  includes:
    in_header: myHeader.tex
---

>>>>

---
title: "Update after major correction to *Management induced changes of soil organic carbon on global croplands*"
author: "Kristine Karstens"
date: "June 8, 2021"
output: pdf_document
rmarkdown::pdf_document:
  fig_caption: yes
---
